---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# holiday.dates

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/Fredo-XVII/holiday.dates?branch=master&svg=true)](https://ci.appveyor.com/project/Fredo-XVII/holiday.dates)
[![R-CMD-check](https://github.com/Fredo-XVII/holiday.dates/workflows/R-CMD-check/badge.svg)](https://github.com/Fredo-XVII/holiday.dates/actions)
[![Github All Releases](https://img.shields.io/github/downloads/Fredo-XVII/holiday.dates/total.svg)]()
<!-- badges: end -->

The goal of holiday.dates is to create a data frame with holiday dates flagged in
a dataframe.  The user has options for the output data frame to be either the days
or weeks between 2 days.  A column of dates can also be passed to the function, 
but it will only use the first and last dates to build the holiday data frame.

[Git Pages Site](https://fredo-xvii.github.io/holiday.dates/)

## Installation

You can install the development version of holiday.dates like so:

``` r
library(remotes)
remotes::install_github("Fredo-XVII/holiday.dates")
```

## Examples

Below you will an example for holidays associated with days.  Notice that in this 
output you get the calendar date as well as the week begin date and the week end 
date.

```{r}

library(holiday.dates)

days_df <- tibble::tibble(weeks = seq.Date(as.Date('2015-01-01'), as.Date('2020-01-01'), by = 'day'))

holiday_data(df = days_df, out_df = "days") %>% head(10)
```


In this example you will see that output for when the `out_df = "week"`.  It is 
the aggregation of the days dataframe up to the week level.  You can see how the
first row relates to the first 7 rows in the data frame above.
```{r example}
library(holiday.dates)

weeks_df <- tibble::tibble(weeks = seq.Date(as.Date('2015-01-01'), as.Date('2020-01-01'), by = 'week'))

holiday_data(df = weeks_df, out_df = "week") %>% head(10)
```

**NOTE:** For those days/weels when there is no holiday the value for holiday name field is `NoHoliday`.
